Figures and Tables

### 2021-02-04 paper/figures_tables.Rmd
minor changes

```{r fig.width=6, fig.height=7}

@@

dispersal_data %>% 
  ggplot() +
  geom_density(aes(x = dispersal, group = id), color = "grey") +
  geom_density(aes(x = dispersal), color = "red") +
  # stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
  facet_wrap(~model, ncol = 3) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)") -> dens_by_id

@@

## Generalized Pareto tail distribution for seed dispersal

```{r}
knitr::kable(evd_table_500)
```

@@

dispersal_data %>% 
  filter(., model == "Null") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
  # geom_function(aes(color = "Individual"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> A

@@

dispersal_data %>% 
  filter(., model == "Individual") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
   geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> AA

@@

dispersal_data %>% 
  filter(., model == "Individual") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
   # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> AAA

@@

plot_grid(C, CC, CCC, nrow = 3, labels = "AUTO")

@@

### Threshold diagnostic plots
```{r}
aligned_plots(null_mrl, null_threshplot, orig_thres, title = "Null model")
aligned_plots(indiv_mrl, indiv_threshplot, orig_thres, title = "Individual model")
aligned_plots(fam_mrl, fam_threshplot, orig_thres, title = "Family model")
```

>>>>

```{r fig.width=6, fig.height=6}

@@

dispersal_data %>% 
  ggplot() +
  geom_density(aes(x = dispersal, group = id), color = "grey70") +
  geom_density(aes(x = dispersal), color = "black") +
  # stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
  facet_wrap(~model, ncol = 3) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)") -> dens_by_id

@@

## Generalized Pareto tail distribution for seed dispersal
Actually, do use the thresholds from the diagnostic plots. These are the parameters with those thresholds.

```{r}

knitr::kable(bind_rows(evd_table %>% 
  mutate(Threshold = c(null_thresh, indiv_thresh, fam_thresh))))

@@

dispersal_data %>% 
  filter(., model == "Null") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Null data"), geom = "line", position = "identity") +
  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
  # geom_function(aes(color = "Individual"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  lims(x = c(0, 1500)) +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> A

@@

dispersal_data %>% 
  filter(., model == "Individual") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Individual data"), geom = "line", position = "identity") +
  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
   geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  lims(x = c(0, 1500)) +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> AA

@@

dispersal_data %>% 
  filter(., model == "Individual") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Family data"), geom = "line", position = "identity") +
  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
   # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  lims(x = c(0, 1500)) +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> AAA

@@

plot_grid(C, CC, CCC, nrow = 3, labels = "AUTO") -> D

ggsave("paper/test.png",
       D,
       width = 6,
       height = 9,
       dpi = 300)

@@

### Threshold diagnostic plots
```{r}

threshplot_fx <- function(thresh_data, th, title = NULL){

  thresh_data %>%
    ggplot(., aes(y = t.scale, x = u.i)) +
    geom_point(shape = 1, size = 2) +
    # geom_line(linetype = "dashed") +
    geom_linerange(aes(x = u.i, ymin = low.t.scale, ymax = up.t.scale)) +
    labs(title = title, x = "Threshold", y = "Scale") +
    theme_bw() +
    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
    geom_vline(xintercept = 500, color = "black", linetype = "dashed") +
    scale_x_continuous(limits = c(0, 700), n.breaks = 7 ) +
    # scale_x_continuous(name = NULL, labels = NULL, breaks = NULL) +
    # theme(axis.title.x = element_blank(),
    #       axis.ticks.x = element_blank(),
    #       axis.text.x = element_blank()) +
    # coord_cartesian(xlim = c(200, 550)) +
    NULL -> thresh_scale

  thresh_data %>%
    ggplot(., aes(y = shape, x = u.i)) +
    geom_point(shape = 1, size = 2) +
    geom_linerange(aes(x = u.i, ymin = low.shape, ymax = up.shape)) +
    labs(x = "Threshold", y = "Shape") +
    theme_bw() +
    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
    geom_vline(xintercept = 500, color = "black", linetype = "dashed") +
    scale_x_continuous(limits = c(0, 700), n.breaks = 7 ) +
    # coord_cartesian(xlim = c(200, 550)) +
    NULL -> thresh_shape

  plot_grid(thresh_scale, thresh_shape, nrow = 2)

}

mrl_plot <- function(mrl_data, title = NULL){

  mrl_data %>%
    ggplot(., aes(x = u.i_mrl, y = `Mean Excess`)) +
    geom_line() +
    geom_line(aes(y = `95% lower`), linetype = "dashed", color = "black") +
    geom_line(aes(y = `95% upper`), linetype = "dashed", color = "black") +
    labs(title = title, x = "Threshold values") +
    scale_x_continuous(n.breaks = ceiling(round(max(mrl_data$u.i_mrl))/100)) +
    theme_bw()
}
aligned_plots <- function(mrl_data, thresh_data, threshold, title = NULL){
  title <- ggdraw() +
    draw_label(
      title,
      fontface = 'bold',
      x = 0,
      hjust = 0
    ) +
    theme(
      # add margin on the left of the drawing canvas,
      # so title is aligned with left edge of first plot
      plot.margin = margin(0, 0, 0, 7)
    )

  plot_grid(mrl_plot(mrl_data) +
              #coord_equal() +
              geom_vline(xintercept = threshold, color = "red", linetype = "dashed") +
              geom_vline(xintercept = 500, color = "black", linetype = "dashed"),
            threshplot_fx(thresh_data, threshold),
            nrow = 2,
            rel_heights = c(2,3),
            labels = "auto") -> actual_plots

  plot_grid(title,
            actual_plots,
            ncol = 1,
            rel_heights = c(0.1,1))
}

# Null
null_thresh <- round(null_mrl$u.i_mrl[15])

# Indiv
indiv_thresh <- round(indiv_mrl$u.i_mrl[15])

# Fam
fam_thresh <- round(fam_mrl$u.i_mrl[15])

aligned_plots(null_mrl, null_threshplot, null_thresh, title = "Null model")
aligned_plots(indiv_mrl, indiv_threshplot, indiv_thresh, title = "Individual model")
aligned_plots(fam_mrl, fam_threshplot, fam_thresh, title = "Family model")
```
